
% This is a modified version of res2.tex found on:
% http://www.rpi.edu/dept/arc/training/latex/resumes/

% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
% the margin option causes section titles to appear to the left of body text
%\topmargin= -0.5in %added this to decrease top margin

% The next 3 lines modify the text box height and distance from top of page.
% See http://en.wikibooks.org/wiki/LaTeX/Page_Layout#Page_dimensions
\voffset=-0.3in
\headheight=0pt
\textheight=10.5in

\textwidth=5.2in % increase textwidth to get smaller right margin

\usepackage{ulem} % needed to make underlines work across hfill's
\usepackage{hyperref} % used for hyperlinks
\usepackage{helvetica} % uses helvetica postscript font (helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{enumitem}
\usepackage{multicol}

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Almir Sarajcic}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{Sarajevo, Bosnia and Herzegovina}
 \moveleft.5\hoffset\centerline{\href{mailto:almir.sarajcic@icloud.com}{almir.sarajcic@icloud.com}}

\begin{resume}

\section{Overview}
  Senior full stack software developer having experience working in several industries: gaming, social media, real estate, finance, education, news etc.

  Technologies I'm familiar with range from backend languages, frameworks and runtimes Elixir, Ruby, PHP, Node.js, Phoenix and Ruby on Rails,
  databases PostgreSQL and MySQL and frontend tools React and vanilla JS.
  Other frontend technologies I've used include React Native, Ionic and Swift.
  I also have experience working with Docker and Kubernetes, nginx and Apache.
  For the deployment I've used Heroku, Render, AWS and Google Cloud.
  I write code in a TDD manner.

  I enjoy working in teams and I prefer small companies.
  I have experience working remotely in startups.
  I also work as a freelancer.

\section{Experience}
\uline{{\bf Full Stack Developer}, Lobbsta, Johannesburg Area (remote)
  \hfill Apr 2020 - present}\vspace{3pt}\\
Lobbsta is an online E-sports platform for professional Dota 2 players. It helps players find teams, book matches and analyze their game performance. I'm helping the team refactor backend and frontend code written in Elixir, Node.js and React and create new features.

\uline{{\bf Backend Developer}, Mukuru, Cape Town (remote)
  \hfill Oct 2016 - Mar 2020}\vspace{3pt}\\
Mukuru is an African fintech startup founded in 2006.
It helps with money transfer around Africa.

I was part of a remote team from Sarajevo. We were working on implementing
new features in PHP application using DDD and TDD, but also improving old code.

\uline{{\bf Full Stack Developer}, Klika, Sarajevo
  \hfill Apr 2015 - Oct 2016}\vspace{3pt}\\
Klika is a software development company offering outsourcing and consulting services. I was working on client projects using Ruby on Rails and JavaScript.

\uline{{\bf Full Stack Developer}, Social Eddy, McAllen, Texas (remote)
  \hfill Sep 2012 - Nov 2013}\vspace{3pt}\\
Social Eddy was a content marketing tool that helped users manage social accounts and curate content. I was hired into remote team to help finishing the application created with PHP, MySQL and Javascript.
\vspace{3pt}
\begin{itemize} \itemsep -1pt % reduce space between lines
  \item Communication with 3rd-party APIs
  \item Analytics
  \item SQL queries optimization
\end{itemize}


\section{Skills}
\begin{multicols}{3}
  \begin{itemize}[label={}, leftmargin=0cm, itemsep=0cm]
      \item Elixir
  \item Phoenix
  \item Ruby
  \item Ruby on Rails
  \item PHP
  \item JavaScript
  \item React
  \item SQL
  \item Redis
  \item PostgreSQL
  \item MySQL
  \item Docker
  \end{itemize}
\end{multicols}

\section{Languages}
\begin{itemize}[label={}, leftmargin=0cm, itemsep=0cm]
  \item Bosnian (native)
  \item English (full professional proficiency)
\end{itemize}

\end{resume}
\end{document}
